---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# idtools

<!-- badges: start -->
<!-- badges: end -->

The goal of package `idtools` is to supply high level helper tools and functions for use for ID Research. Additional packages used for ID Research are likely to depend on the functions in this package.

## Installation

You can install the development version of idtools like so:

``` r
devtools::install_github('wf-id/idtools')
```

## Shorthand Example

Using a shorthand function, `g()` instead of `dplyr::glimpse()`:

```{r shorthand}
library(idtools)

#glimpse the mtcars dataset with shorthand

g(mtcars)


```


## Template Example

Using the `generate_template()` function:

```{r template}
library(idtools)

#create a temp file that uses glue syntax for demonstration
tmp <- tempfile()
writeLines("My birthday is in the month of {my_month}", con = tmp)
my_month <- "March"


#read in a template file with glue syntax
out <- generate_template(tmp)

print(out)


```
